Transforming Trash as an Artistic Act

### 2015-12-06 chapter1_reduced.tex
reduction
Former-commit-id: c9bcc8bcd3f9852bbc75b9d9620cfb397ada7b06

%
%
[Every.] \paraphrase{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others \cite{zimring2012encyclopedia}.}

Trash in every age and every society. Refuse is part of people's consumption practices and it is very common concept from developed cities to rural areas, from modern societies to ancient societies\cite[p.33]{rathje1992rubbish} \todo{more ref.}. For archaeologist dumps are one the significant places to figure how people consume in the ancient times \todo{ref}.

Trash is everywhere and, produced every time. During daily activities such as drinking coffee, eating beverages, waiting in the bank trash is generated. The pattern is spread to the all day and different places. It is hard to say that any location(place) is waste free. Nearly every place people require waste bin. If we do not find a waste bin, people often leave it (to the ground?). Production of trash never stops.

Trash is everywhere. Trash is in the streets, in your home, in the sea that you swam, rotating around the globe \footnote{Satellite discards leaved the atmosphere and they rotate around the globe like satellites.}. Even if trash is tried to be moved away from people life, it is close as closest waste bin.

%
%
% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
[Facts.] \paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD\footnote{OECD(Organization for Economic Co-operation and Development) is an international economic organization of 34 countries. Turkey is member of this organization.} countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.} \todo{Zengin adamın harcama lüksü}

\comment{Bunu neden diyorsun? Teze nasıl bir katkı sağlıyor?}

%
%
[Common.] (In the dictionary \todo{Which dictionary?} trash means anything useless, worthless or discarded. In parallel to this definition, common perception is to get rid of them as soon as possible. People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore. People want to refuse them from their lives most of the time not thinking beyond (or alternative). However to establish solid understanding of trash (or trashing things), we have to give attention to the trash (and ask why it is trash). \comment{(To understand the beyond common perception we have to ask...)} How does it become trash? \comment{Is it possible to do something other than refusing them?}

@@

Trash moves, objects moves from place to place. From homes to garbage trucks. From streets to land fills. From garbage baskets to sculptures. Lots of different people touches to trash. With the trash what moves? Trash moves around. Travels like humans. Travels like commodities. When we are telling about the travel of commodities, then it is easy to say that trashes also moves around.

People do not think what happens after they throw trash away. \paraphrase{They forget about it and don’t think about all the time and energy and money put into disposing of it.} It exits from people's life but not the world. It is stacked to another place.

A project conducted by MIT researches journey of trash by placing trackers onto the trash \cite{chen2009mit}. The results are surprising. Trashes spread away across the country and this journey takes month. Further it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo[inline]{footnote what are these countries?}. In other words American's trash is not only their trash. As commodities spread to the every corner of the world, trash also. What happens when it is traveled to the other countries, how they approaches these items. \comment{They find new uses and meanings on them.} \todo[inline]{consider African native}

%
%
[Aspects. Approaches.] In this thesis study to understand the different aspects of trash is a key element. Sometimes it is accepted as a problem (for examples keeping streets clean, handling the smell) that is need to carefully and seriously managed. On the other hand it is accepted as a source of diversity. Further for the recyclers it is a source of income. The economical aspect of trash can not ignored. There are people who collects plastics, scraps and papers from waste bins and landfills. By collecting and selling them they endure their life. Further some of the countries \todo{ref.} imports garbage to recycle or use their own purposes. As it can be seen clearly there are different aspects and approaches to the trash. For some people it is disgusting thing and moved away from living space and for the others source of their life. \paraphrase{While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared \cite{zimring2012encyclopedia}.}

[Relative.] As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}. She realized that any of them called the practice as recycling. For them using trash again and again is very natural and it is part of their life. On the contrary for the developed countries trash considered as a thing that must be avoided. There is no place for trash in their life. It can be understood that approach to the trash is not same for the all regions of world \todo{ref}.

@@

[Production of trash and removal of trash.] For example a project conducted by MIT Sensible City Lab. reveals the \quotes{removal-chain} of objects by tracking trash with the mobile trackers places onto the trash \cite{chen2009mit}.

%
%
[Parts of us.] \paraphrase{Our trash is a testament; what we throw away says much about our values, our habits, and our lives \cite{zimring2012encyclopedia}. Our trash is part of us, whether or not we choose to acknowledge it \cite{zimring2012encyclopedia}. The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream \cite{zimring2012encyclopedia}.}

%
%
[Change in the production and consumption practices.] \paraphrase{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption. Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.} As the result of it amount of goods boost and the cost of them significantly reduced. Things once reused again and again, now thrown away because it is more affordable to replace \todo{daha uygun bir kelime bul} with new one. \paraphrase{Mass production and commodification liquidated what remained of folkways tied to local production, demanding people construct the meaning of their lives through purchases rather than production. (FROM Collage Culture)} As the production increased its by-product material waste is also increased. \paraphrase{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption. (Trash Culture)} \todo{Ref: Trash Culture}

@@

%
%
[Art] \paraphrase{At least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art.} \todo{Bu nereden?}

@@

\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature.}

%
%
[Different types of trash] There are different types of trashes. Result of different production and consumption practices different trashes are generated. For example \paraphrase{radioactive waste is usually a by-product of nuclear power generation and other applications of nuclear fission or nuclear technology}. Electronic waste (e-waste), Construction and demolition waste, Medical waste are one of them. As it can be seen that there are lots of different types and as various as activities of human. In this scope of thesis \ldots \todo{Ben hangisini kullanacağım. Buna burada değinmek gerekli mi?}

@@

Increasing ecological concerns is one of the aspects of trash. As most of trash last decades are not easily decomposable. Relases toxics and other things.

@@

As many people are inside the business of transforming trash through craft and so on. People on the streets looking for aluminum cans, glass bottles, plastic. They collect and sell them to survive. There are companies that are collect waste materials to regain them again the industry. In thesis they are not in the scope. People that give attention to the trash and behave artistic act is in the scope of this thesis.

%
%
[Scope] Human discard. In the scope of trash not biodegradable trash is considered. Produced, industrial commodities are considered.

@@

% TODO Move to chapter 4.
\comment{Research and the found samples of works helped a lot to shape my work. They provide me deeper understanding of the subject and what I am doing and they lead me during the development of the work.}

@@

%
%****************************************
\section{A Note on Terminology}
Many scholars and authors have used different words (or terminology) to define trash\todo{bunun yerine başka bir şey demek gerekir mi?}. Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter are some of them. Although there are slight differences between these words, sometimes they are used to signify same concept (or used with the same purposes). It signifies that the topic is so broad and there is no consensus on terminology. Words are used interchangeably. From the book \quotes{Rubbish: the Archeology of Garbage} gives clearer definition of some these words:

@@

\comment{Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash. Analysis of them may be subject of another thesis.}

>>>>

%
%
\comment{[Every.]}
\paraphrase{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes \cite{zimring2012encyclopedia}.}

Trash exists in every age and every society. Refuse is part of people's consumption practices and it is a very common concept from developed cities to rural areas, from modern societies to ancient societies\cite[p.33]{rathje1992rubbish} \todo{more ref.}. For archaeologist dumps are one the significant places to figure how people consume in the ancient times \todo{ref}.

Trash is everywhere and, produced every time. During daily activities such as drinking coffee, eating beverages, waiting in the bank trash is generated. Different aspects of our life, eating, drinking, working, traveling, all of them are leave behind wastes and that become invisible. We are surrounded by all kinds of consumer goods. We are consuming everywhere while walking, working and traveling. The pattern is spread to all day and different places. It is hard to say that any (place) is waste free. Nearly every place people require waste bin. If people do not find a waste bin, people often leave it (to the ground?). Production of trash never stops. It is inseparable from people's activities.

Trash is everywhere. Trash is in the streets, in your home, in the sea that you swam, rotating around the globe \footnote{Satellite discards leaved the atmosphere and they rotate around the globe like satellites.}. Even if trash is tried to be moved away from people life, it is close as nearest waste bin.

\comment{[Global.]}
\paraphrase{It is not limited with geography, ethnicity, gender, nationality. The process of retrieving and transforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban America as well as the remotest corners of the world.}

%
% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
\comment{[Facts.]}
\paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD\footnote{OECD(Organization for Economic Co-operation and Development) is an international economic organization of 34 countries. Turkey is a member of this organization.} countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.}

% Üstteki kısmı neden diyorsun? Teze nasıl bir katkı sağlıyor? Throw away culture a taşınabilir.
% From recycled book.
\paraphrase{A person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away. America is one of the greatest country in terms of generating trash and exporting them to the other third world, fourth world countries.\cite{cerny1996recycled}}

%
%
\comment{[Common.]}
(In the dictionary \todo{Which dictionary?} trash means anything useless, worthless or discarded. In parallel to this definition, common perception is to get rid of them as soon as possible. People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore. People want to refuse them from their lives most of the time not thinking beyond (or alternative). However to establish solid understanding of trash (or trashing things), we have to give attention to the trash (and ask why it is trash). \comment{(To understand the beyond common perception we have to ask...)} How does it become trash? \comment{Is it possible to do something other than refusing them?}

@@

Trash moves, objects moves from place to place. From homes to garbage trucks. From streets to landfills. From waste bins to sculptures. Lots of different people touches to trash. With the trash what moves? Travels like humans. Travels like commodities. When we are telling about the travel of commodities, then it is easy to say that trashes also moves around. \todo{summarize here. ve bir yere bağla.}

People do not think what happens after they throw trash away. \paraphrase{They forget about it and don’t think about all the time and energy and money put into disposing of it.} It exits from people's life but not from the world. It is stacked to another place.

A project conducted by MIT researches journey of trash by placing trackers onto the trash \cite{chen2009mit}. The results are surprising. Trashes spread away across the country and this journey takes month. Further it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo[inline]{footnote what are these countries?}. In other words American's trash is not only their trash. As commodities spread to the every corner of the world, trash also. What happens when it is traveled to the other countries, how they approaches these items. \comment{They find new uses and meanings on them.} \todo{consider African native}

%
%
\comment{[Aspects. Approaches.]}
In this thesis study to understand the different aspects of trash is a key element. Sometimes it is accepted as a problem (for examples keeping streets clean, handling the smell) that is need to carefully and seriously managed. On the other hand it is accepted as a source of diversity. Further for the recyclers it is a source of income. The economical aspect of trash can not ignored. There are people who collects plastics, scraps and papers from waste bins and landfills. By collecting and selling them they endure their life. Further some of the countries \todo{ref.} imports garbage to recycle or use their own purposes. As it can be seen clearly there are different aspects and approaches to the trash. For some people it is disgusting thing and moved away from living space and for the others source of their life. \paraphrase{While dictionary definitions of garbage describe it as \quotes{filth} and \quotes{worthless}, scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared \cite{zimring2012encyclopedia}.}

\comment{[Relative.]}
As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}. She realized that any of them called the practice as recycling. For them using trash again and again is very natural and it is part of their life. On the contrary for the developed countries trash considered as a thing that must be avoided. There is no place for trash in their life. It can be understood that approach to the trash is not same for the all regions of world \todo{ref}.

@@

\comment{[Production of trash and removal of trash.]}
For example a project conducted by MIT Sensible City Lab. reveals the \quotes{removal-chain} of objects by tracking trash with the mobile trackers places onto the trash \cite{chen2009mit}.

%
%
\comment{[Parts of us.]}
\paraphrase{Our trash is a testament; what we throw away says much about our values, our habits, and our lives \cite{zimring2012encyclopedia}. Our trash is part of us, whether or not we choose to acknowledge it \cite{zimring2012encyclopedia}. The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream \cite{zimring2012encyclopedia}.}

%
%
\comment{[Change in the production and consumption practices.]}
\paraphrase{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption. Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.} As the result of it amount of goods boost and the cost of them significantly reduced. Things once reused again and again, now thrown away because it is more affordable to replace \todo{daha uygun bir kelime bul} with new one. \paraphrase{Mass production and commodification liquidated what remained of folkways tied to local production, demanding people construct the meaning of their lives through purchases rather than production. (FROM Collage Culture)} As the production increased its by-product material waste is also increased. \paraphrase{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption. (Trash Culture)} \todo{Ref: Trash Culture}

@@

%
%
\comment{[Art]}
\paraphrase{At least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art.} \todo{Bu nereden?}

@@

\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature.} \todo{ref missing.}

% TODO new comer
\paraphrase{This thesis seeks to answer the following questions: How did art and literature respond to this age of consumption? What do the productions and practices of artists and writers reveal about the meaning of mass production, consumption, reification (depersonalization), mechanical reproduction, and meaning? (FROM Collage Culture)}

Do people want to take back (or revisit) the trash once thrown away? The purpose is to turn them to a things that worth to reconsider.

Questioned that how do artists reflect garbage and what are their tactics?

%
%
[Different types of trash] There are different types of trashes result of different production and consumption practices. For example \paraphrase{radioactive waste is usually a by-product of nuclear power generation and other applications of nuclear fission or nuclear technology}. Electronic waste (e-waste), Construction and demolition waste, Medical waste are one of them. As it can be seen that there are lots of different types and as various as activities of human. In this scope of thesis focused on disposable items and paper trash.

@@

@@

As many people are inside the business of transforming trash through craft and so on. People on the streets looking for aluminum cans, glass bottles, plastic. They collect and sell them to survive. There are companies that are collect waste materials to regain them to the industry. In thesis they are not in the scope. People that give attention to the trash and behave artistic act is in the scope of this thesis.

% TODO new comer
% PERCEPTION TO THE TRASH, DICIPLINES
\comment{WASTE AND TECHNOLOGY RELATIONSHIP} \quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}. In other word the problem is our technology which is not perfect. (and I'm not sure that at some point that technology will reach to the perfection or not.)

% TODO new comer
\comment{TECHNICAL PROBLEM, NEED TO MANAGED, RECYCLING (CAPITALISM), UPCYCLING} \paraphrase{On the contrary, with respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework. The enormous quantities of waste accumulating in urban centers, Hawkins writes in “Plastic Bags,” were not only taken as a threat to the environment, but also as a sign of an individualistic, insensitive, and hedonistic consumer society. Waste now became evil. If the environment is to be saved from our destructive power, then waste should be “managed,” Hawkins asserts. Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world. Upcycling... On the other side of the coin is the business stemming from these practices; recyclers not only ease their conscience through recycling; they also make a profit. Recycling, as “the huge tertiary sector devoted to getting rid of things, is central to the maintenance of capitalism; it doesn’t just allow economies to function by removing excess and waste—it is an economy, realizing commercial value in what’s discarded,” Hawkins and Muecke write in Culture and Waste. In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home. In short, there is a whole sector of upcycling now.} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}

% TODO new comer
\comment{DESIGN, ALTERNATIVE DICIPLINE.} \paraphrase{Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless. People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}

% TODO new comer
\comment{UPCYCLING, sample thesis statement sentence} \paraphrase{This article is about those objects that are recreated from trash through the process of upcycling. Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” I argue that design, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste. This theory counters the argument that an object is dead once it is disposed of.} \todo[inline]{Reference, (Trashion: The Return of the Disposed by Bahar Emgin).}

% TODO new comer
% FROM Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\comment{OTHER DICIPLINE, INDUSTRY} \paraphrase{the process of re fabrication explored here is not to be confused with the kind of industrial strength recycling to which we in the West are most accustomed. When we think of recycling in America and other industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers. returned to the industrial process. solid waste management, global greening, and ecological awareness are the buzzwords that guide and motivate consumers and industries to engage in this process of secondary and post consumer waste recycling.}

@@

@@

%
%****************************************
\section{A Note on Terminology}
Many scholars and authors have used different words (or terminology) to define trash. Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter are some of them. Although there are slight differences between these words, sometimes they are used to signify same concept (or used with the same purposes). It signifies that the topic is so broad and there is no consensus on terminology. Words are used interchangeably. From the book \quotes{Rubbish: the Archeology of Garbage} gives clearer definition of some these words:

@@
